Comparing OTU quality across clustering strategies

### 2021-07-01 exploratory/2021/algorithm_diagram.Rmd
Enforce node order

```{r ggraph_mod}
# devtools::install_github('kelly-sovacool/ggraph', ref = 'iss-297_ggtext')
#library(ggraph) # something is wrong & this fails, but load_all() works!
devtools::load_all('../ggraph')
library(ggtext)
library(tidygraph)
```
```{r ggraph_exp}
graph <-
  tbl_graph(nodes = data.frame(name = c("A B C", "D E F", "G **H** I", "J K L")),
            edges = data.frame(from = c(2, 2, 2), 
                               to = c(3, 4, 2), 
                               mcc = c(0.97, 0.84, 0.80)))
ggraph(graph, layout = 'linear') +
  geom_edge_arc(aes(label = mcc,
                    start_cap = label_rect(node1.name),
                    end_cap = label_rect(node2.name)), 
                arrow = arrow(length = unit(4, 'mm')),
                edge_colour = 'gray',
                angle_calc = 'along',
                label_dodge = unit(2, 'mm')
                ) +
  geom_edge_loop(aes(label = mcc,
                     span=120,
                     direction=270,
                     strength=0.5
                     ),
                 angle_calc = 'along',
                 label_dodge = unit(-2, 'mm'),
                 edge_colour = 'gray') +
  geom_node_label(aes(label = name), richtext = TRUE) +
  theme(panel.background = element_rect(fill='white'))
```

>>>>

```{r ggraph_mod}
# devtools::install_github('kelly-sovacool/ggraph', ref = 'iss-297_ggtext')
#library(ggraph) # something is wrong & this fails, but load_all() works!
devtools::load_all('../ggraph')
library(ggtext)
library(tidygraph)
library(patchwork)
g1 <-
  tbl_graph(nodes = data.frame(name = c("A B C", "D E F", "G **H** I", "J K L"),
                               i = 1:4),
            edges = data.frame(from = c(2, 2, 2), 
                               to = c(3, 4, 2), 
                               mcc = c(0.97, 0.84, 0.80)) %>% 
              mutate(is_link = from == to))
g2 <-
  tbl_graph(nodes = data.frame(name = c("A B C", "D **E** F", "G H I", "J K L"),
                               i = 1:4),
            edges = data.frame(from = c(2, 2, 2), 
                               to = c(1, 3, 2), 
                               mcc = c(0.94, 0.81, 0.86)) %>% 
              mutate(is_link = from == to))
g2_ranks <-
  tbl_graph(nodes = data.frame(name = c("A B C", "D **E** F", "G H I", "J K L")),
            edges = data.frame(from = c(1, 2, 3), 
                               to = c(2, 3, 4)))
```

```{r ggraph_exp, fig.dim=c(6.8,1)}
plot_graph <- function(graph) {
  create_layout(graph, 'linear', sort.by = i) %>% 
  ggraph() +
  geom_edge_arc(aes(label = mcc,
                    start_cap = label_rect(node1.name),
                    end_cap = label_rect(node2.name)), 
                arrow = arrow(length = unit(4, 'mm'),
                              type = 'closed'),
                edge_colour = 'gray',
                angle_calc = 'along',
                label_dodge = unit(-2, 'mm')
                ) +
  geom_edge_loop(aes(span = 1, direction = 270, strength = 0.1, color = is_link)) +
  geom_node_label(aes(label = name)) +
    scale_color_manual(c('black', 'white')) +
  theme_void() +
  theme(plot.margin=unit(x=c(0,0,0,0), units="pt"))
}

pg1 <- plot_graph(g1) 
pg2 <- plot_graph(g2)

pg1 / pg2
```
